Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-08-16 Latex/journal_v1/V5/pr.tex
add sth

Assume we have two types of eMBB service instances. In figure \ref{fig:9}, the aggregate throughput (by considering the priority factor $\delta_s$) is depicted for two eMBB service instances. Here we consider 4 UEs in each service. We assume that the the fronthaul link and the end-to-end delay have no restrictions.
The figure \ref{fig:9} presented that by increasing the priority factor for one service instance, more resources are allocated to this service instance, and the aggregate throughput of this service is increased and vice versa. Also, we can realize from this figure that the aggregate throughput has the most significant value at the same priority.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{priorityLast.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for two eMBB service instances vs. Priority of the first service instance }
  \label{fig:9}
\end{figure}

In the figure \ref{fig:10}, the aggregate throughput is presented vs. the number of UEs for one service in a system by considering two different cloud restrictions and fronthaul restrictions.
In the graph of cloud restriction, we have the restrictions in O-DU and O-CU.
In the graph of fronthaul restriction, we have the restrictions in O-RU.
In the O-RU restriction graph, we assume that the fronhaul link is set to be 47 bits/sec/Hz (the variance of quantization noise is $10^{-13}$) , and the maximum power of each O-RU is 40 dBm. Also, the maximum power of each UE is set to be 35 dBm. Moreover, the minimum data rate for each UE in this service is 6 bits/sec/Hz. In this graph, we assume that there is less restriction in the end-to-end delay (50 ms) and the VNF resources (the system has 100 reserved VNF).
In the graph of cloud restriction, we assume that there is no restriction on the fronthaul link.
The limitation on the power is less than the graph of fronthaul limitation, and it is set to be 45 dBm on the power of each O-RU, and the maximum power of each UE is 40 dBm.
The minimum data rate for each UE in this service is 10 bits/sec/Hz. 
The end-to-end delay for each UE is 4ms and the mean arrival rate is 2Mbps. 
and the mean service rate is 10Mbps.
In this figure, the consequence of cloud limitation and fronthaul limitation is depicted.
As the number of UEs increases, the aggregate throughput rises linearly, and the graph of cloud restriction increases more than the other graph of fronthaul limitation.

\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{AcloudVsFronthaul.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput vs. Number of UEs in a Service}
  \label{fig:10}
\end{figure}
In figure \ref{fig:11}, the aggregate throughput is shown according to the number of iteration (outer loop) of the
proposed algorithm (IABV) for different numbers of UEs for one service. In this figure, the convergence of the IABV method is illustrated. The minimum data rate for each UE is assumed to be 2 Mbps.
After four iterations, IABV converges to the fixed value.

@@

%\subsection{Summary of Simulation Results}
In figure 12, the aggregate throughput is shown according to the number of UEs for two different methods, namely the
proposed algorithm (IABV) and the optimal method for URLLC service.
The minimum data rate is 5bits/sec/Hz for each UE and the maximum delay is $0.1$ms.
Also the mean arrival rate is set to be $0.2$Mbps and the mean service rate is $0.5$Mbps.
The other parameters are depicted in table \ref{table:1a}.
The optimal approach is obtained from the two-step joint exhaustive search and using CVX. 
In each iteration in the first step, the PRB allocation and O-RU association are obtained from brute force, and in the second step, we use CVX to get optimal power.
Our solution is close to the optimal value in a small number of UEs.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{optimal1.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput vs. Number of UEs }
  \label{fig:12}
\end{figure}
\section{Conclusion}\label{conc}
This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services i.e eMBB, mMTC, and, URLLC.
The isolation of various types of services i.e eMBB, mMTC, and, URLLC in the O-DU, the O-CU, and the user plane function (UPF) is accomplished.
Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput. The limited fronthaul capacity and the mean end-to-end delay for each service are considered. 
The problem is mixed-integer non-linear programming that is solved by the two-step iterative algorithm.
In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then we obtain PRB association and power allocation using the Lagrangian method.
Then in the second step, the O-RU association is acquired.
The performance of our proposed method (IABV) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
Also, we assume distinct scenarios for each service i.e eMBB, mMTC, and, URLLC based on their requirement QoS.
Simulation results depict that the proposed method (IABV) achieved $18.6\%$ higher data rate than the baseline scheme.
Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than FBDR and the baseline scheme.

>>>>

Assume we have two types of eMBB service instances. In figure \ref{fig:9}, the aggregate throughput (by considering the priority factor $\delta_s$) is depicted for two eMBB service instances. Here we consider 4 UEs in each service. We assume that the the fronthaul link and the end-to-end delay have no restrictions.
The figure \ref{fig:9} presented that by increasing the priority factor for one service instance, more resources are allocated to this service instance, and the aggregate throughput of this service is increased and vice versa. Also, we can realize from this figure that the aggregate throughput has the most significant value at the same priority.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{priorityLast.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for two eMBB service instances vs. Priority of the first service instance }
  \label{fig:9}
\end{figure}
%
%In the figure \ref{fig:10}, the aggregate throughput is presented vs. the number of UEs for one service in a system by considering two different cloud restrictions and fronthaul restrictions.
%In the graph of cloud restriction, we have the restrictions in O-DU and O-CU.
%In the graph of fronthaul restriction, we have the restrictions in O-RU.
%In the O-RU restriction graph, we assume that the fronhaul link is set to be 47 bits/sec/Hz (the variance of quantization noise is $10^{-13}$) , and the maximum power of each O-RU is 40 dBm. Also, the maximum power of each UE is set to be 35 dBm. Moreover, the minimum data rate for each UE in this service is 6 bits/sec/Hz. In this graph, we assume that there is less restriction in the end-to-end delay (50 ms) and the VNF resources (the system has 100 reserved VNF).
%In the graph of cloud restriction, we assume that there is no restriction on the fronthaul link.
%The limitation on the power is less than the graph of fronthaul limitation, and it is set to be 45 dBm on the power of each O-RU, and the maximum power of each UE is 40 dBm.
%The minimum data rate for each UE in this service is 10 bits/sec/Hz. 
%The end-to-end delay for each UE is 4ms and the mean arrival rate is 2Mbps. 
%and the mean service rate is 10Mbps.
%In this figure, the consequence of cloud limitation and fronthaul limitation is depicted.
%As the number of UEs increases, the aggregate throughput rises linearly, and the graph of cloud restriction increases more than the other graph of fronthaul limitation.

%\begin{figure}
%  \centering 
%    \includegraphics[scale = 0.4]{AcloudVsFronthaul.eps}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Aggregate Throughput vs. Number of UEs in a Service}
%  \label{fig:10}
%\end{figure}
In figure \ref{fig:11}, the aggregate throughput is shown according to the number of iteration (outer loop) of the
proposed algorithm (IABV) for different numbers of UEs for one service. In this figure, the convergence of the IABV method is illustrated. The minimum data rate for each UE is assumed to be 2 Mbps.
After four iterations, IABV converges to the fixed value.

@@

%\subsection{Summary of Simulation Results}
In figure \ref{fig:12}, the aggregate throughput is shown according to the number of UEs for two different methods, namely the
proposed algorithm (IABV) and the optimal method for URLLC service.
The minimum data rate is 5bits/sec/Hz for each UE and the maximum delay is $0.1$ms.
Also the mean arrival rate is set to be $0.2$Mbps and the mean service rate is $0.5$Mbps.
The other parameters are depicted in table \ref{table:1a}.
The optimal approach is obtained from the two-step joint exhaustive search and using CVX. 
In each iteration in the first step, the PRB allocation and O-RU association are obtained from brute force, and in the second step, we use CVX to get optimal power.
Our solution is close to the optimal value in a small number of UEs.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{optimal1.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput vs. Number of UEs }
  \label{fig:12}
\end{figure}
\section{Conclusion}\label{conc}
This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services i.e eMBB, mMTC, and, URLLC.
The isolation of various types of services i.e eMBB, mMTC, and, URLLC in the O-DU, the O-CU, and the user plane function (UPF) is accomplished.
Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput. The limited fronthaul capacity and the mean end-to-end delay for each service are considered. 
The problem is mixed-integer non-linear programming that is solved by the two-step iterative algorithm.
In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then we obtain PRB association and power allocation using the Lagrangian method.
Then in the second step, the O-RU association is acquired.
The performance of our proposed method (IABV) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
Also, we assume distinct scenarios for each service i.e eMBB, mMTC, and, URLLC based on their requirement QoS.
Simulation results depict that the proposed method (IABV) achieved $18.6\%$ higher data rate than the baseline scheme.
Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than FBDR and the baseline scheme.
